\documentclass[12pt]{letter}
\setlength{\textheight}{9.0in}
\setlength{\textwidth}{6.0in}
\setlength{\topmargin}{-0.4in}

\begin{document}

\pagestyle{empty}

\begin{letter}

\vspace{0.2in}
\centerline{\bf Code Abstract for CVODE v2.2.0}

\begin{enumerate}

\item {\bf Identification}

Software acronym: CVODE v2.2.0

Short title: Stiff/nonstiff ODE integrator.

\item {\bf Developer name(s) and affiliations}

Alan C. Hindmarsh and Radu Serban (CASC, LLNL)

\item {\bf Software Completion Date}

November 19, 2004

\item {\bf Brief description}

CVODE is a general purpose (serial and parallel) initial value ordinary differential 
equation solver for both stiff and nonstiff systems.

\item {\bf Method of solution}

Integration is by Adams or BDF methods, at user option. Corrector iteration is by 
functional iteration or Newton iteration. For the solution of linear systems within 
Newton iteration, users can select a dense solver, a band solver, a diagonal 
approximation, or a preconditioned GMRES solver.

\item {\bf Computer(s) for which software is written}

CVODE should run on any computer with an ANSI C compiler. The appropriate 
precision (single, double, or extended) is selected at the configuration phase.

For use with Fortran applications, a set of Fortran/C interface routines,
called FKINSOL, is also supplied.  These are written in C, but assume that
the user calling program and all user-supplied routines are in Fortran.

\item {\bf Operating system}

No system-dependency in the software itself. But installation is system-dependent. 
The package supplied consists of a single archived file. Installation from this file 
assumes a UNIX system with the tar utility. Configuration is done through a 
configure script. Compilation of libraries is done by way of UNIX makefiles.

\item {\bf Programming language(s) used}

ANSI C (100\%)

\item {\bf Software limitations}

none

\item {\bf Unique features of the software}

CVODE is organized in a highly modular manner. The basic integrator
is separate from, and independent of, the linear system 
solvers, as well as the vector operation modules. Thus the set of linear solvers can be 
expanded and the internal vector representation can be replaced with no impact on 
the main solver.


\item {\bf Related and auxiliary software}

CVODE is part of SUNDIALS (Suite of Nonlinear and Differential/Algebraic equation 
Solvers). 

\item {\bf Other Programming or Operating Information or Restrictions}

none


\item {\bf Hardware Requirements}

none


\item {\bf Time Requirements}

Timing is highly dependent on machine and problem.


\item {\bf References}

Document provided with the distribution
\begin{itemize}
\item A. C. Hindmarsh and R. Serban, "User Documentation for CVODE v2.2.0," 
      LLLNL technical report UCRL-SM-208108, November 2004.
\item A. C. Hindmarsh and R. Serban, "Example Programs for CVODE v2.2.0," 
    LLNL technical report UCRL-SM-208110, November 2004.
\end{itemize}
Additional background references
\begin{itemize}
\item A. C. Hindmarsh, P. N. Brown, K. E. Grant, S. L. Lee, R. Serban, 
    D. E. Shumaker, and C. S. Woodward, "SUNDIALS, Suite of Nonlinear and 
    Differential/Algebraic Equation Solvers," ACM Trans. Math. Softw., 
    accepted, 2004.
\item S.D. Cohen and A.C. Hindmarsh, "CVODE, a Stiff/nonstiff ODE Solver in C,"
    Computers in Physics, 10(2), pp. 138-143, 1996.
\end{itemize}
\end{enumerate}

\end{letter}
\end{document}