\documentclass[12pt]{letter}
\setlength{\textheight}{9.0in}
\setlength{\textwidth}{6.0in}
\setlength{\topmargin}{-0.4in}

\begin{document}

\pagestyle{empty}

\begin{letter}

\hfill November 19, 2004

\vspace{0.2in}
\centerline{\bf Memorandum}

\noindent{\bf TO}: Reviewers of CVODES \\
\noindent{\bf FROM}: Radu Serban, Alan C. Hindmarsh \\
\noindent{\bf SUBJECT}: Software release for CVODES

CVODES is a general purpose (serial and parallel) initial value ordinary 
differential equation (ODE) solver with sensitivity analysis capabilities. 
It solves both stiff and nonstiff systems and provides both forward and 
adjoint sensitivity analysis options. 
CVODES was developed within CASC under ASCI-PSE and MICS-SciDAC support. 
It is not usable in stand-alone form; it must be combined with an application program.

At this time we wish to release a new version of CVODES (v2.1.0) for the 
following reasons:
\begin{itemize}
\item To promote research collaborations between CASC personnel and colleagues at 
      other sites, collaborations in which CVODES will be useful as a research tool;
\item To elicit feedback from outside users which could lead to enhancements that will 
      benefit LLNL users as well;
\item To enhance the external reputation of CASC and LLNL with respect to 
      mathematical software written here.
\end{itemize}

CVODES shares a common design philosophy and a number of support modules with the 
other solvers in the Suite of Nonlinear and Differential/Algebraic equation Solvers (SUNDIALS), 
namely CVODE, IDA, and KINSOL, all of which have been previously released for unlimited 
distribution.

Being an item for general-purpose mathematical software, CVODES is not expected to be 
subject to export controls on the basis of its intrinsic capabilities. 
No fundamentally new functionality has been added since the previous version released
(v1.0, UCRL-CODE-2002-046).

A brief abstract of the package is provided in the Code Abstract. 


\vspace{0.5in}                 
\hfill Radu Serban, CASC

\vspace{0.5in}                 
\hfill Alan C. Hindmarsh, CASC

\end{letter}
\end{document}