\documentclass[12pt]{letter}
\setlength{\textheight}{9.0in}
\setlength{\textwidth}{6.0in}
\setlength{\topmargin}{-0.4in}

\begin{document}

\pagestyle{empty}

\begin{letter}

\vspace{0.2in}
\centerline{\bf Code Abstract for sundialsTB v2.1.1}

\begin{enumerate}

\item {\bf Identification}

Software acronym: sundialsTB v2.1.1

Short title: Matlab MEX-binding for SUNDIALS v2.1.1

\item {\bf Developer name(s) and affiliations}

Radu Serban (CASC, LLNL)

\item {\bf Software Completion Date}

May 09, 2005

\item {\bf Brief description}

sundialsTB is a Matlab interface to the SUNDIALS (Suite of Nonlinear, Algebraic/Differential
equation Solvers). 

\item {\bf Method of solution}

The core of each sundialsTB interface is a MEX file which wraps around various
user-callable SUNDIALS functions. Communication Matlab-C is bidirectional, in the
sense that both the program driver and various user-provided functions are to be
supplied in Matlab.

\item {\bf Computer(s) for which software is written}

sundialsTB should run on any computer with an ANSI C compiler (for building the
SUNDIALS libraries) and with the Matlab software installed.

Optionally, for parallel support, LAM-MPI v > 7.1.1 is required (for MPI-2 features,
in particular spawning dynamic processes).

\item {\bf Operating system}

No system-dependency in the software itself. But installation is system-dependent. 
The package supplied consists of a single archived file. Installation from this file 
assumes a UNIX system with the tar utility. Compilation of libraries is done by way 
of UNIX makefiles.

\item {\bf Programming language(s) used}

ANSI C and Matlab scripting

\item {\bf Software limitations}

none

\item {\bf Unique features of the software}

sundialsTB combines the ease of use of the Matlab environment with the flexible
and robust solvers in SUNDIALS. As such, it provides several valuable extensions
to the integrators already available in Matlab, in particular sensitivity analysis
capabilities, both forward and adjoint.


\item {\bf Related and auxiliary software}

sundialsTB is build on top of SUNDIALS (Suite of Nonlinear and Differential/Algebraic 
equation Solvers). For parallel support, it uses mpiTB, an MPI toolbox for Matlab.

\item {\bf Other Programming or Operating Information or Restrictions}

none


\item {\bf Hardware Requirements}

none


\item {\bf Time Requirements}

Timing is highly dependent on machine and problem.


\item {\bf References}

Document provided with the distribution
\begin{itemize}
\item R. Serban, "sundialsTB, a Matlab Interface to SUNDIALS," 
      LLLNL technical report UCRL-SM-xxxxxx, May 2005.
\end{itemize}
Additional background references
\begin{itemize}
\item A. C. Hindmarsh and R. Serban, "User Documentation for CVODES v2.1.0," 
    LLNL technical report UCRL-SM-208111, November 2004.
\item A. C. Hindmarsh and R. Serban, "Example Programs for CVODES v2.1.0," 
    LLNL technical report UCRL-SM-208115, November 2004.
\item A. C. Hindmarsh and R. Serban, "User Documentation for IDA v2.2.0," 
    LLNL technical report UCRL-SM-208112, November 2004.
\item A. C. Hindmarsh and R. Serban, "Example Programs for IDA v2.2.0," 
    LLNL technical report UCRL-SM-208113, November 2004.
\item A. M. Collier, A. C. Hindmarsh, R. Serban, and C. S. Woodward,
    "User Documentation for KINSOL v2.2.0," LLNL technical report
    UCRL-SM-208116, November 2004. 
\item A. M. Collier and R. Serban, "Example Programs for KINSOL v2.2.0,"
    LLNL technical report UCRL-SM-208114, November 2004.
\item A. C. Hindmarsh, P. N. Brown, K. E. Grant, S. L. Lee, R. Serban, 
    D. E. Shumaker, and C. S. Woodward, "SUNDIALS, Suite of Nonlinear and 
    Differential/Algebraic Equation Solvers," ACM Trans. Math. Softw., 
    accepted, 2004.
\end{itemize}
\end{enumerate}

\end{letter}
\end{document}