\documentclass[12pt]{letter}
\setlength{\textheight}{9.0in}
\setlength{\textwidth}{6.0in}
\setlength{\topmargin}{-0.4in}

\begin{document}

\pagestyle{empty}

\begin{letter}

\hfill May 9, 2005

\vspace{0.2in}
\centerline{\bf Memorandum}

\noindent{\bf TO}: Reviewers of sundialsTB \\
\noindent{\bf FROM}: Radu Serban \\
\noindent{\bf SUBJECT}: Software release for sundialsTB

sundialsTB is a Matlab interface to the SUNDIALS solvers providing MEX-binding to 
the user-callable and user-supplied functions required by the SUNDIALS solvers.
sundialsTB was developed within CASC under MICS-SciDAC support. 
It is not usable in stand-alone form; it must be used from within Matlab.

At this time we wish to release sundialsTB (v2.1.1) for the following reasons:
\begin{itemize}
\item To promote research collaborations between CASC personnel and colleagues at 
      other sites, collaborations in which sundialsTB will be useful as a research tool;
\item To further the flexibility and usability of the SUNDIALS solvers, which already
      have hundreds of users, both at LLNL, as well as at other DOE laboratories and
      universities.
\item To elicit feedback from outside users which could lead to enhancements that will 
      benefit LLNL users as well;
\item To enhance the external reputation of CASC and LLNL with respect to 
      mathematical software written here.
\end{itemize}

sundialsTB is completely dependent on the solvers in the Suite of Nonlinear and 
Differential/Algebraic equation Solvers (SUNDIALS), namely CVODES, IDA, and KINSOL, 
all of which have been previously released for unlimited distribution (open-source,
BSD licenses).

Being an item for general-purpose mathematical software, sundialsTB is not expected to be 
subject to export controls on the basis of its intrinsic capabilities.

A brief abstract of the package is provided in the Code Abstract. 


\vspace{0.5in}                 
\hfill Radu Serban, CASC

\end{letter}
\end{document}