%% foo.tex
\begin{samepage}
\hrule
\begin{center}
\phantomsection
{\large \verb!IDAQuadSetOptions!}
\label{p:IDAQuadSetOptions}
\index{IDAQuadSetOptions}
\end{center}
\hrule\vspace{0.1in}

%% one line -------------------

\noindent{\bf \sc Purpose}

\begin{alltt}
IDAQuadSetOptions creates an options structure for IDAS.
\end{alltt}

\end{samepage}


%% definition  -------------------

\begin{samepage}

\noindent{\bf \sc Synopsis}

\begin{alltt}
function options = IDAQuadSetOptions(varargin) 
\end{alltt}

\end{samepage}

%% description -------------------

\noindent{\bf \sc Description}

\begin{alltt}
IDAQuadSetOptions creates an options structure for IDAS.

   Usage: OPTIONS = IDAQuadSetOptions('NAME1',VALUE1,'NAME2',VALUE2,...)
          OPTIONS = IDAQuadSetOptions(OLDOPTIONS,'NAME1',VALUE1,...)

   OPTIONS = IDAQuadSetOptions('NAME1',VALUE1,'NAME2',VALUE2,...) creates 
   an IDAS options structure OPTIONS in which the named properties have 
   the specified values. Any unspecified properties have default values. 
   It is sufficient to type only the leading characters that uniquely 
   identify the property. Case is ignored for property names. 
   
   OPTIONS = IDAQuadSetOptions(OLDOPTIONS,'NAME1',VALUE1,...) alters an 
   existing options structure OLDOPTIONS.
   
   IDAQuadSetOptions with no input arguments displays all property names 
   and their possible values.
   
IDAQuadSetOptions properties
(See also the IDAS User Guide)

ErrControl - Error control strategy for quadrature variables [ on | {off} ]
   Specifies whether quadrature variables are included in the error test.
RelTol - Relative tolerance for quadrature variables [ scalar {1e-4} ]
   Specifies the relative tolerance for quadrature variables. This parameter is
   used only if QuadErrCon=on.
AbsTol - Absolute tolerance for quadrature variables [ scalar or vector {1e-6} ]
   Specifies the absolute tolerance for quadrature variables. This parameter is
   used only if QuadErrCon=on.

SensDependent - Backward problem depending on sensitivities [ {false} | true ]
   Specifies whether the backward problem quadrature right-hand side depends
   on forward sensitivites. If TRUE, the right-hand side function provided for
   this backward problem must have the appropriate type (see IDAQuadRhsFnB).

   See also
        IDAQuadInit, IDAQuadReInit.
        IDAQuadInitB, IDAQuadReInitB
\end{alltt}






\vspace{0.1in}