%% foo.tex
\begin{samepage}
\hrule
\begin{center}
\phantomsection
{\large \verb!CVodeQuadSetOptions!}
\label{p:CVodeQuadSetOptions}
\index{CVodeQuadSetOptions}
\end{center}
\hrule\vspace{0.1in}

%% one line -------------------

\noindent{\bf \sc Purpose}

\begin{alltt}
CVodeQuadSetOptions creates an options structure for quadrature integration with CVODES.
\end{alltt}

\end{samepage}


%% definition  -------------------

\begin{samepage}

\noindent{\bf \sc Synopsis}

\begin{alltt}
function options = CVodeQuadSetOptions(varargin) 
\end{alltt}

\end{samepage}

%% description -------------------

\noindent{\bf \sc Description}

\begin{alltt}
CVodeQuadSetOptions creates an options structure for quadrature integration with CVODES.

   Usage: OPTIONS = CVodeQuadSetOptions('NAME1',VALUE1,'NAME2',VALUE2,...)
          OPTIONS = CVodeQuadSetOptions(OLDOPTIONS,'NAME1',VALUE1,...)

   OPTIONS = CVodeQuadSetOptions('NAME1',VALUE1,'NAME2',VALUE2,...) creates 
   a CVODES options structure OPTIONS in which the named properties have 
   the specified values. Any unspecified properties have default values. 
   It is sufficient to type only the leading characters that uniquely 
   identify the property. Case is ignored for property names. 
   
   OPTIONS = CVodeQuadSetOptions(OLDOPTIONS,'NAME1',VALUE1,...) alters an 
   existing options structure OLDOPTIONS.
   
   CVodeQuadSetOptions with no input arguments displays all property names 
   and their possible values.
   
CVodeQuadSetOptions properties
(See also the CVODES User Guide)

ErrControl - Error control strategy for quadrature variables [ {false} | true ]
   Specifies whether quadrature variables are included in the error test.
RelTol - Relative tolerance for quadrature variables [ scalar {1e-4} ]
   Specifies the relative tolerance for quadrature variables. This parameter is
   used only if ErrControl = true.
AbsTol - Absolute tolerance for quadrature variables [ scalar or vector {1e-6} ]
   Specifies the absolute tolerance for quadrature variables. This parameter is
   used only if ErrControl = true.

SensDependent - Backward problem depending on sensitivities [ {false} | true ]
   Specifies whether the backward problem quadrature right-hand side depends
   on forward sensitivites. If TRUE, the right-hand side function provided for
   this backward problem must have the appropriate type (see CVQuadRhsFnB).


   See also
        CVodeQuadInit, CVodeQuadReInit.
        CVodeQuadInitB, CVodeQuadReInitB
\end{alltt}






\vspace{0.1in}